Online Multiclass Linear Classification with Bandit Feedback

### 2019-01-17 ICML-submission/from-weak-separability-to-strong-separability.tex
Some fixes in section 5.1

\begin{theorem}[Margin transformation]
\label{theorem:margin-transformation}
Let $(x_1, y_1)$, $(x_2, y_2)$, $\dots$, $(x_T, y_T)$ in $\B(0,1) \times
\{1,2,\dots,K\}$ be a sequence of labeled examples that is weakly linearly
separable with margin $\gamma > 0$. Let $\phi$ be as defined in
equation~\eqref{equation:phi} and let
\begingroup
\allowdisplaybreaks
\begin{align*}
r & = 2 \left\lceil \frac{1}{4} \log_2(4K-3) \right\rceil + 1, \quad \quad s = \left \lceil \log_2(2/\gamma) \right \rceil, \\
\gamma_1 & = \frac{1}{2\sqrt{K}}  \\
& \ \cdot \left(376 \lceil \log_2(2K-2) \rceil \cdot \left \lceil \sqrt{\frac{2}{\gamma}} \right \rceil \right)^{-\frac{1}{2} \lceil \log_2(2K-2) \rceil \cdot \left \lceil \sqrt{\frac{2}{\gamma}} \right \rceil}, \\
\gamma_2 & = \frac{2^{s(s+1)r(K-1)} }{4\sqrt{K}(4K-5) 2^{K-1}} \\
& \ \cdot \left(2^{s+1} r(K-1) (4s+2)^2 \right)^{-(s+1/2)r(K-1)} \; .
\end{align*}
\endgroup
Then, the sequence of labeled examples transformed by $\phi$,
namely $(\phi(x_1), y_1), (\phi(x_2), y_2), \dots,
(\phi(x_T), y_T)$, is strongly linearly separable with margin $\gamma' =
\max\{\gamma_1, \gamma_2\}$. In addition, for all $t$ in $\cbr{1,\ldots,T}$,
$k(x_t,x_t) \leq 2$.
\end{theorem}
%$\norm{\phi(x_1)}_{\ell_2},
%\norm{\phi(x_2)}_{\ell_2}, \dots, \norm{\phi(x_T)}_{\ell_2} \le 2$

@@

\paragraph{Overview.} The idea behind the construction and analysis of the mapping
$\phi$ is polynomial approximation. Specifically, we give $k$ polynomials $p_1$,
$\ldots$, $p_k$, such that:
\begin{align}
\label{equation:poly-pos}
& \forall t \in \cbr{1,2,\dots,T}, p_{y_t}(x_t) \ge \frac{\gamma'}2 \; ,
\\
\label{equation:poly-neg}
& \begin{gathered}
\forall t \in \cbr{1,2,\dots,T} \ \forall i \in \cbr{1,2,\ldots,K} \setminus \cbr{y_t} \\
p_i(x_t) \leq -\frac{\gamma'}2 \; .
\end{gathered}
\end{align}
As each polynomial $p_i$ can be written as $\ip{c_i}{\phi(x)}$ for some $c_i \in
\ell_2$, it immediately shows that the set of examples $(\phi(x_1),y_1), \ldots,
(\phi(x_T),y_T)$ is strongly linear separable.

To construct $p_1, p_2, \dots, p_k$ that satisfy
Equations~\eqref{equation:poly-pos} and~\eqref{equation:poly-neg}, we consider
constructing each $p_i$ separately. Specifically, $p_i$ needs to satisfy that:
\begin{align}
\label{equation:poly-pos-i}
\forall t \in \cbr{1,2,\dots,T}, y_t = i \Rightarrow p_i(y_t) \ge \frac{\gamma'}2 \; , \\
\label{equation:poly-neg-i}
\forall t \in \cbr{1,2,\dots,T}, y_t \neq i \Rightarrow p_i(y_t) \le -\frac{\gamma'}2 \; .
\end{align}

Under the weak linear separability assumption, we note that all examples from
class $i$ lie in
\[ R_i^+ = \bigcap_{j \in \cbr{1,\ldots,K} \setminus \cbr{i}} \cbr{x: \norm{x} \le 1, \ip{w_i^* - w_j^*}{x} \geq \gamma}, \] and all examples from the remaining classes lie in
\[ R_i^- = \bigcup_{j \in \cbr{1,\ldots,K} \setminus \cbr{i}} \cbr{x: \norm{x} \le 1, \ip{w_i^* - w_j^*}{x} \leq  -\gamma}. \]
Therefore, to satisfy Equations~\eqref{equation:poly-pos-i}
and~\eqref{equation:poly-neg-i}, it suffices to construct $p_i$ such that:
\begin{align}
x \in R_i^+ & \Rightarrow p_i(x) \ge \frac {\gamma'} 2
\label{eqn:r-plus}
\\
x \in R_i^- & \Rightarrow p_i(x) \le - \frac {\gamma'} 2
\label{eqn:r-minus}
\end{align}

>>>>

\begin{theorem}[Margin transformation]
\label{theorem:margin-transformation}
Let $(x_1, y_1)$, $(x_2, y_2)$, $\dots$, $(x_T, y_T)$ in $\B(0,1) \times
\{1,2,\dots,K\}$ be a sequence of labeled examples that is weakly linearly
separable with margin $\gamma > 0$. Let $\phi$ be as defined in
equation~\eqref{equation:phi} and let
\begingroup
\allowdisplaybreaks
\begin{align*}
r & = 2 \left\lceil \frac{1}{4} \log_2(4K-3) \right\rceil + 1, \quad \quad s = \left \lceil \log_2(2/\gamma) \right \rceil, \\
\gamma_1 & = \frac{1}{2\sqrt{K}}  \\
& \ \cdot \left(376 \lceil \log_2(2K-2) \rceil \cdot \left \lceil \sqrt{\frac{2}{\gamma}} \right \rceil \right)^{-\frac{1}{2} \lceil \log_2(2K-2) \rceil \cdot \left \lceil \sqrt{\frac{2}{\gamma}} \right \rceil}, \\
\gamma_2 & = \frac{2^{s(s+1)r(K-1)} }{4\sqrt{K}(4K-5) 2^{K-1}} \\
& \ \cdot \left(2^{s+1} r(K-1) (4s+2)^2 \right)^{-(s+1/2)r(K-1)} \; .
\end{align*}
\endgroup
Then, the sequence of labeled examples transformed by $\phi$,
namely $(\phi(x_1), y_1), (\phi(x_2), y_2), \dots,
(\phi(x_T), y_T)$, is strongly linearly separable with margin $\gamma' =
\max\{\gamma_1, \gamma_2\}$. In addition, for all $t$ in $\cbr{1,\ldots,T}$,
$k(x_t,x_t) \leq 2$.
\end{theorem}

@@

\paragraph{Overview.} The idea behind the construction and analysis of the
mapping $\phi$ is polynomial approximation. Specifically, we construct $K$
multivariate polynomials $p_1, p_2, \dots,p_K$ such that:
\begin{align}
\label{equation:poly-pos}
& \forall t \in \cbr{1,2,\dots,T}, p_{y_t}(x_t) \ge \frac{\gamma'}{2} \; ,
\\
\label{equation:poly-neg}
& \begin{gathered}
\forall t \in \cbr{1,2,\dots,T} \ \forall i \in \cbr{1,2,\ldots,K} \setminus \cbr{y_t} \\
p_i(x_t) \le - \frac{\gamma'}{2} \; .
\end{gathered}
\end{align}
We then show (\autoref{lemma:norm-bound}) that each polynomial $p_i$ can be
expressed as $\ip{c_i}{\phi(x)}_{\ell_2}$ for some $c_i \in \ell_2$. This
immediately implies that that the examples $(\phi(x_1),y_1), \ldots,
(\phi(x_T),y_T)$ are strongly linearly separable with margin $\gamma'$.

The conditions \eqref{equation:poly-pos} and~\eqref{equation:poly-neg} are
equivalent to that
\begin{align}
\label{equation:poly-pos-i}
\forall t \in \cbr{1,2,\dots,T}, y_t = i \quad \Rightarrow \quad p_i(y_t) \ge \frac{\gamma'}{2} \; , \\
\label{equation:poly-neg-i}
\forall t \in \cbr{1,2,\dots,T}, y_t \neq i \quad \Rightarrow \quad p_i(y_t) \le -\frac{\gamma'}{2} \; .
\end{align}
hold for all $i \in \{1,2,\dots,K\}$. We can thus fix $i$ and focus on
construction of one particular polynomial $p_i$.

Since examples $(x_1,y_1), (x_2, y_2), \dots, (x_T,y_T)$ are weakly linearly separable,
all examples from class $i$ lie in
$$
R_i^+ = \!\!\!\!\! \!\!\!\!\! \bigcap_{j \in \cbr{1,2,\dots,K} \setminus \cbr{i}} \cbr{x \in \B(0,1) ~:~ \ip{w_i^* - w_j^*}{x} \ge \gamma},
$$
and all examples from the remaining classes lie in
$$
R_i^- = \!\!\!\!\! \!\!\!\!\! \bigcup_{j \in \cbr{1,2,\dots,K} \setminus \cbr{i}} \cbr{x \in \B(0,1) ~:~ \ip{w_i^* - w_j^*}{x} \le -\gamma}.
$$
Therefore, to satisfy conditions~\eqref{equation:poly-pos-i}
and~\eqref{equation:poly-neg-i}, it suffices to construct $p_i$ such that:
\begin{align}
\label{eqn:r-plus}
x \in R_i^+ & \Rightarrow p_i(x) \ge \frac {\gamma'} 2 \\
\label{eqn:r-minus}
x \in R_i^- & \Rightarrow p_i(x) \le - \frac {\gamma'} 2
\end{align}
